---
output:
  html_document: default
  pdf_document: default
  word_document: default
---

---
title: "DDP_R Markdown, Leaflet"
author: "MatyusI"
date: '14 april 2017 '

## R Markdown
## Peer-graded Assignment: R Markdown and Leaflet
## Instructions

###Create a web page using R Markdown that features a map created with Leaflet.

###Host your webpage on either GitHub Pages, RPubs, or NeoCities.

###Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity! Review criterialess

###The rubric contains the following two questions:
###Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?
###Does the web page feature an interactive map that appears to have been created with Leaflet?

##Load the library
```{r}
library(leaflet)
```
## Warning: package 'leaflet' was built under R version 3.3.2
```{r}
mymap <- leaflet() %>% addTiles() 
```
## Point the location
## lat=47.547928, lng=19.0743122


```{r}
mymap <- mymap %>% addMarkers(lat=47.547928, lng= 19.0743122, popup="OTP BANK _BUDAPEST, HUNGARY")
mymap
```

